---
title: "Tika Test"
author: "Gaurav Chaturvedi"
date: "9/23/2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
print_lines <- function (a, num_lines) {
long=length(a)
m <- min(long, num_lines)
for (i in 1:m){
    print(a[i])
}
}
```

## Tika Test

This is a test of the Open Source OCR Tool called Tika. 

Tika is a linux library that claims to have parsers and readers across formats JPG/PNG/PDF etc. 

So lets test it out with:
- PDF (XML)
- Images 


## Tika with PDF (XML) 1

So let us test how Tika does with a PDF (XML). This is a paper on bitcoin technology (bitcoin.pdf)

```{r pdf_xml1, echo=FALSE}
command <- "java"
args <- c('-jar', '/home/ubuntu/tika/tika-1.13/tika-app/target/tika-app-1.13.jar', 
          '-t', 'file:///home/ruser/tika-ocr/bitcoin.pdf') # if file use file:///home/ub..
stderr <- '/home/ruser/tika-ocr/stderr.txt'
a <- system2(command, args=args, stdout=TRUE, stderr=stderr)
print_lines(a, 10)
```

Notes:

- Tika does fairly well with plain text (headers etc.)
- Images are ignored (including text in images) 
- Mathematical symbols are distorted 


## Tika with PDF (XML) 2

Let us test how Tika does with a PDF (XML) with tables. This is a CPF statement 

```{r pdf_xml2, echo=FALSE}
command <- "java"
args <- c('-jar', '/home/ubuntu/tika/tika-1.13/tika-app/target/tika-app-1.13.jar', 
          '-t', 'file:///home/ruser/tika-ocr/cpfcon.pdf') # if file use file:///home/ub..
stderr <- '/home/ruser/tika-ocr/stderr.txt'
a <- system2(command, args=args, stdout=TRUE, stderr=stderr)
print_lines(a, 20)
```

Notes:

- Tika does fairly well in extracting both the header and the table (although header appears at the bottom)
- Table is still formatted, the spaces have been padded with a '.'
- It will be easy to extract key information from this 

## Tika with Image (with text) 1

Let us test how Tika does with a image with text 

```{r pdf_img1, echo=FALSE}
command <- "java"
args <- c('-jar', '/home/ubuntu/tika/tika-1.13/tika-app/target/tika-app-1.13.jar', 
          '-t', 'file:///home/ruser/tika-ocr/img1.gif') # if file use file:///home/ub..
stderr <- '/home/ruser/tika-ocr/stderr.txt'
system2(command, args=args, stdout=TRUE, stderr=stderr)
```

Notes:

- The output is blank. Tika could not extract text from the image 

## Tika with Image (with text) 2

Let us test how Tika does with a image with text (this is a scanned pdf)

```{r pdf_img2, echo=FALSE}
command <- "java"
args <- c('-jar', '/home/ubuntu/tika/tika-1.13/tika-app/target/tika-app-1.13.jar', 
          '-t', 'file:///home/ruser/tika-ocr/scanned.pdf') # if file use file:///home/ub..
stderr <- '/home/ruser/tika-ocr/stderr.txt'
system2(command, args=args, stdout=TRUE, stderr=stderr)
```

Notes:

- The output is blank. Tika could not extract text from the image 


## Conclusion 

Tika is good at extracting text from PDF (XML) documents only. It does not work well with images / scanned pdfs. 

